msc dissertation

### 2021-08-10 msc dissertation code.Rmd
latest

##no idea why it doesn't show groups (control vs treatment) so I merge original condition to the new one

@@

##no idea why it doesn't show groups (control vs treatment) so I merge original condition to the new one

@@

glm42 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
glm421 <- glm(measurement ~ condition + condition*headlineveracity, data = attention2, family = binomial(link = "logit"))

@@

ggplot(p1, aes(x = condition, y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9))
```

>>>>

##no idea why it doesn't show condition column (control vs treatment) so I merge original condition to the new one

@@

##no idea why it doesn't show conditions (control vs treatment) so I merge original condition to the new one

@@

glm42 <- glm(measurement ~ condition + headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))
glm421 <- glm(measurement ~ condition + condition*headlineveracity + attentioncheck, data = attention2, family = binomial(link = "logit"))

@@

ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
  xlab("Condition") + 
  ylab("Likelihood of Sharing (%)") +
  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
  scale_fill_discrete(name = "Headline Veracity", labels = c("Fake", "Real"))
